SoK: Defending Against Web Application Attacks: From Research Approaches to Practical Tools

### 2014-11-14 docs/questioning.tex
updated picture to cover CSRF properly. Also added corresponding description in the model.

An attacker can initiate an injection attack through two different main routes.
One way is to use the browser of a victim as an attack
vehicle, through which the code will be injected in the application.
For example, the attacker could craft a malicious script into a {\sc
  url} and then trick a user to click on it through social
engineering, e.g., by sending a phishing email (transition {\sc p-xss} 1.1, {\sc
  n-xss} 1.1, {\sc csrf} 1). Alternatively, the attacker may be able
to inject directly the malicious code on the server through an HTTP request
({\sc dsl} 1, {\sc p-xss} 1, {\sc n-xss} 1). This would happen
in a web application that accepts and processes user input
without appropriate validation. An attacker could upload data
containing a specially crafted script
to steal the cookies of the visiting users ({\sc p-xss} 1, {\sc n-xss} 1)
or embed malicious
{\sc sql} code to retrieve the password entries from a database ({\sc dsl} 1).
%Recall the examples we provided in Section~\ref{sec:attacks}.
Note that {\sc xss} attacks can start from both routes.

@@

In the case of a {\sc csrf} attack, consider a
user who visits a page, where attackers have managed
to inject {\sc html} code that contains a hidden
request in the way we described in Section~\ref{sec:attacks}.
If an authenticated user visits this web page, then the
malicious request will reach the application ({\sc csrf} 2) and
the functionality dictated by the malicious response will
be performed.

>>>>

An attacker can initiate an injection attack through two different main routes.
One way is to use the browser of a victim as an attack
vehicle, through which the code will be injected in the application.
For example, the attacker could craft a malicious script into a {\sc
  url} and then trick a user to click on it through social
engineering, e.g., by sending a phishing email (transition {\sc p-xss} 1.1, {\sc
  n-xss} 1.1). Alternatively, the attacker may be able
to inject directly the malicious code on the server through an {\sc http} request
({\sc dsl} 1, {\sc p-xss} 1, {\sc n-xss} 1, {\sc csrf} 1). This would happen
in a web application that accepts and processes user input
without appropriate validation. An attacker could upload data
containing a specially crafted script
to steal the cookies of the visiting users ({\sc p-xss} 1, {\sc n-xss} 1),
an {\tt img} tag including a malicious {\sc http} request ({\sc csrf}),
or embed malicious
{\sc sql} code to retrieve the password entries from a database ({\sc dsl} 1).
%Recall the examples we provided in Section~\ref{sec:attacks}.
Note that {\sc xss} attacks can start from both routes.

@@

A common {\sc csrf} attack could involve just a
{\sc url} containing a malicious {\sc http} request
which in turn must be clicked by the user
(via social engineering again).
However, this technique does not involve code injection
and it is not described in Figure~\ref{fig:attacks}.
The {\sc csrf} attack illustrated here could
involve an attacker that manages to inject
{\sc html} code that contains a hidden request
in the way we described in Section~\ref{sec:attacks}.
This code will be stored in the database ({\sc csrf} 5)
and then it will re-enter the application if
a user visits a page ({\sc csrf} 6). When the
content reaches the browser the functionality
dictated by the malicious request will be performed.
